---
title: "Shiny Application and Reproduciblle Pitch"
author: "Derek Geng"
date: "20 augustus 2017"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,comment = NA)
```

## Background

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Introduction
This application uses `diamonds` data from ggplot2 and has the function to predict the price of a diamond depending of its properties.

- Carat size
- Cut level
- Color type

```{r echo=FALSE,message=FALSE, warning=FALSE}
library(ggplot2)
library(plotly)
data("diamonds")

diam <- diamonds[,c(1:3,7)]
summary(diam)
```

## Plot

```{r,,message=FALSE, warning=FALSE}
plot_ly(diam,x=~ carat, y = ~ price, type = "scatter", color = ~factor(cut))
```


## Application functionality

You can select specific features of the diamond (carat, cut,  color). The application will predict the price of the diamond based on the according features.

Below the link for application: (https://derekgeng.shinyapps.io/shinyapp/)

## Source Code

- `ui.R`
- `server.R`

Both files can be found here: ()
